DOM Review Summary

### 2024-03-15 Analysis/ReviewSummary/ReviewSummary.qmd
clean objectives
Cleaned objective data, added year strata

```{r StudyDetails_years}
studyDetails_clean |>
  filter(!is.na(YearStrata)) |>
  mutate(YearStrata = fct(YearStrata,
                          levels = c("2000-2005", "2006-2010",
                                     "2011-2015", "2016-2020",
                                     "2021-2023"))) |>
  summarise(Articles = n(), .by = YearStrata) |>

@@

Counting by the location of the first author's institution, `{r} nrow(countriesTable` countries are represented in the sample. A strong majority of articles were published by first authors based in the United States of America.

@@

The most frequent category of authorship was academic, with `{r} max(authorCategories_overall)`% of articles having at least one author from an academic institution.

@@

>>>>

```{r StudyDetails_years}
#| echo: false

studyDetails_clean |>
  filter(!is.na(YearStrata)) |>
  mutate(YearStrata = fct(YearStrata,
                          levels = c("2000-2005", "2006-2010",
                                     "2011-2015", "2016-2020",
                                     "2021-2023"))) |>
  summarise(Articles = n(), .by = YearStrata) |>

@@

Counting by the location of the first author's institution, `{r} nrow(countriesTable)` countries are represented in the sample. A strong majority of articles were published by first authors based in the United States of America.

@@

The most frequent category of authorship was academic, with `{r} max(authorCategories_overall$Proportion)` % of articles having at least one author from an academic institution.

@@

```{r Objectives_clean}
#| echo: false

review_Objectives |>
  filter(Status == "Complete") |> 
  select(ID, Obj_Methods, Obj_Future, Obj_Spatial, Obj_Hypothesis) |>
  pivot_longer(cols = c(Obj_Methods, Obj_Future, 
                        Obj_Spatial, Obj_Hypothesis), 
               names_to = "Objective", 
               values_to = "Stated") |>
  mutate(Objective = str_extract(Objective, "(?<=Obj\\_).+"),
         Stated = case_when(Stated == "Y" ~ TRUE,
                            Stated == "N" ~ FALSE)) |>
  left_join(select(studyDetails_clean, ID, Year, YearStrata), by = "ID")
